\documentclass[letterpaper]{article}
\usepackage[margin=1in,bottom=.5in,includefoot]{geometry}

\usepackage{lastpage} 		 % -- Package used for finding total page numbers
\usepackage{amssymb}		 % -- Package used for typing "bold" math letters and symbols
\usepackage{amsmath}		 % -- Package for various math symbols
\usepackage{arydshln}		 % -- Package used for dashed lines in tables
\usepackage{dashrule}		 % -- Package used for dashed lines on the page
\usepackage{listings}		 % -- Package used for code snippets
\usepackage[final]{pdfpages} % -- Package used for inserting pages of a PDF file

% ---------------------------------------------------------------------------------------------
% Edit this section to create the title, headers, and footers for the document
% ---------------------------------------------------------------------------------------------

\newcommand{\authorName}	{Wryn Wagner}
\newcommand{\phone}		{\textsf{(720)557-5443}}
\newcommand{\email}		{\textsl{wagner.wryn@gmail.com}}
\newcommand{\github}		{\textsl{github.com/w0ryn}}
\newcommand{\assignmentDate}	{11/26/2018}
\newcommand{\myMajor}		{Computer Science}
\newcommand{\myMinor}		{Mathematics}

% ---------------------------------------------------------------------------------------------
% Edit this section to modify resume content
% ---------------------------------------------------------------------------------------------

\newcommand{\coverLetter} {
	\noindent To whom it may concern:\\
	
	\noindent I am currently studying under the professional computer science program with Utah State University as an undergraduate on track to graduate in the year 2020. While studying, I am looking for challenging and practical experience where I can learn from mentors and contribute to the Space Dynamics Lab.\\
	
	\noindent Since the first "Hello World" I made as a kid, my passion for computer science and mathematics has only grown. This semester I had my first opportunity to delve into graph theory and its proofs and applications which is an exciting new dimension of problem solving. Particularly in discrete mathematics and algorithms classes I am on the edge of my seat as each new topic seems to answer old questions and open new ones.\\
	
	\noindent For 2 years I was a missionary stationed in Rosario Argentina, where I spent the entirety of my time in small, poverty-stricken towns. I learned to read, write, and speak Spanish as I served the people, and the experience changed my life perspective and helped me appreciate other cultures.\\
	
	\noindent When I'm not working or studying, I like to ride my bike, then come home and cook a nice meal. I toss a mean pizza! If I have a weekend free, I also enjoy a night of board games with friends.\\\\
	
	\noindent Thank you so much for your time and consideration! 
}

% ---------------------------------------------------------------------------------------------
% ------ Header Code --------------------------------------------------------------------------

\newcommand{\headerLeft}	{: \assignmentDate}
\newcommand{\headerCenter}	{}
\newcommand{\headerRight}	{\authorName\ :: \phone}
\newcommand{\pageOfTotal}	{\thepage\ of \pageref{LastPage}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\headerLeft}
\fancyhead[R]{\headerRight}
\fancyhead[C]{\headerCenter}
\fancyfoot[C]{\pageOfTotal}
\fancypagestyle{plain}{
	\fancyhf{}
	\fancyhead[L]{\headerLeft}
	\fancyhead[R]{\headerRight}
	\fancyhead[C]{\headerCenter}
	\fancyfoot[C]{\pageOfTotal}
}

\title{Resume}

\author{
	\authorName \\
	\begin{small}
		\textit{\myMajor\ Major and \myMinor\ Minor}
	\end{small}\\
	\noindent\rule{2in}{0.4pt}\\
	\email \\
	\phone
}

\date{\assignmentDate}

% ---------------------------------------------------------------------------------------------
% ---------------------------------------------------------------------------------------------
% ---------------------------------------------------------------------------------------------

\begin{document}

\maketitle

% ---------------------------------------------------------------------------------------------
% Begin Resume
% ---------------------------------------------------------------------------------------------
\section{Cover Letter} %Problem 1

\coverLetter

\noindent\rule{2in}{0.4pt}

% ---------------------------------------------------------------------------------------------

\clearpage

\section{Education}

\subsection{Current Studies}
\textbf{Undergraduate Computer Science Major and Mathematics Minor: } I will graduate in 2020.

\subsection{Relevant Coursework}
\textbf{Recently Completed (Fall 2018): } Discrete Mathematics (MATH3310). Developing Dynamic, Database-Driven, Web Applications (CS2610). Algorithms and Data Structures (CS2420). Introduction to Event Driven Programming and GUI's (CS2410).\\

\noindent\textbf{Currently Enrolled (Spring 2019): } Advanced Algorithms (CS5050). Introduction to Software Engineering (CS3450). Operating Systems and Concurrency (CS3100). Computer Systems Organization and Architecture (CS2810).

\subsection{Club Involvement}

\textbf{HackUSU -- Organizer/Mentor and Website Maintenance: } Helped prepare and direct the annual Hackathon for USU in 2018. I work with another student to overhaul and currently maintain the website for the club (www.hackusu.org). Planning included weekly board meetings and contacting sponsors and potential sponsors \\

\noindent\textbf{Aggie Game Nights -- Board Member: } I am one of four board members in charge of "Aggie Game Night," which is a club partnered with a local game shop to provide a chance for students to build community and play board games together each week. My responsibilities include weekly board meetings, collection of voting results, weekly announcements, and other club maintenance and decision making. 

\noindent\rule{2in}{0.4pt}

% ---------------------------------------------------------------------------------------------

\section{Skills}

\textbf{Programming Languages: } The following are languages in which I consider myself familiar and proficient: \textit{C++, JavaScript, Java, PHP, Python}. 

I am also familiar with some common frameworks of JavaScript such as \textit{Vue.js, jQuery, jQuery-UI, Bootstrap,} and \textit{Node.js}\\

\noindent\textbf{Software: } I am well-versed in the use of basic computer software including the complete Microsoft Office suite, \LaTeX, Slack, Trello, and Git.\\

\noindent\textbf{Communication and Language: } I am a skilled public speaker, and value strong team communication. I am fluent in Spanish both written and oral.

\noindent\rule{2in}{0.4pt}

% ---------------------------------------------------------------------------------------------

\section{Work History}
\subsection{Barista - Smith's/Starbucks}
\textbf{Dates: } May 2018 to current date\\
\textbf{Description: } Maintain the Starbucks coffee shop, including cleaning, sales, and preparation of food and drink.

\subsection{Full-time Missionary}
\textbf{Dates: } October 2015 until October 2017\\
\textbf{Description: } I was positioned in Argentina to complete daily planning, proselyting, and record keeping. A large part of my time was spent serving others in need and helping clean up after severe flooding in the area.

\subsection{Internship -- SevOne}
\noindent\textbf{Dates: } January 2014 until summer of that same year\\
\noindent\textbf{Description: } Through a high school internship program, I created a PHP coding solution to ingest performance data into the SevOne platform for Comcast and Zayo. 

\subsection{Mathematics Tutor}
\textbf{Dates: } August 2012 until May 2014\\
\textbf{Descripton: } Private tutoring for topics of mathematics ranging from Algebra to Calculus.

\subsection{'Lifeguard II' -- Highlands Ranch Community Association}
\noindent\textbf{Dates: } August 2011 until May 2014\\
\noindent\textbf{Description } While watching over and maintaining the pool areas, it was also my job to render primary aid for all incidents throughout the facility. Weekly training and international lifeguard licensing was required.

\noindent\rule{2in}{0.4pt}

% ---------------------------------------------------------------------------------------------

\section{References}

% first column

\begin{minipage}[t]{0.5\textwidth}

\noindent\textbf{Professor Dave Brown}\\
\textit{Relationship: } Mathematics Professor
\begin{lstlisting}
	david.e.brown@usu.edu
	(435)797-3224
\end{lstlisting}

\hdashrule[0.5ex]{4cm}{1pt}{1pt}\\

\noindent\textbf{Professor Erik Falor}\\
\textit{Relationship: } Computer Science Professor
\begin{lstlisting}
	erik.falor@usu.edu
	(435)797-4118
\end{lstlisting}

\hdashrule[0.5ex]{4cm}{1pt}{1pt}\\

\noindent\textbf{Professor Haitao Wang}\\
\textit{Relationship: } Computer Science Professor
\begin{lstlisting}
	Haitao.Wang@usu.edu
	(435)797-2416
\end{lstlisting}

\hdashrule[0.5ex]{4cm}{1pt}{1pt}\\

\end{minipage}

\begin{minipage}[t]{0.5\textwidth}

\noindent\textbf{Angel Reyes}\\
\textit{Relationship: } Current Employer / Direct Supervisor
\begin{lstlisting}
	angel214.reyes@gmail.com
	(435)535-1720
\end{lstlisting}

\hdashrule[0.5ex]{4cm}{1pt}{1pt}\\

\noindent\textbf{Greg Stanton}\\
\textit{Relationship: } Family Friend
\begin{lstlisting}
	Gregandlars@gmail.com
	(303)717-0710
\end{lstlisting}

\hdashrule[0.5ex]{4cm}{1pt}{1pt}\\

\end{minipage}

\end{document}
