% ---------------------------------------------------------------------
% - To anyone who has found this,                                     -
% ---------------------------------------------------------------------
% -                                                                   -
% - A special welcome to you! Throughout the comments you'll find my  -
% - "unabridged" resume. This includes a variety of accomplishments   -
% - which I'm proud of. Some of these accomplishments are no longer   -
% - relevant to my resume, but some of them just make the darn thing  -
% - too long. Feel free to reach out to me with any questions.        -
% -                                                                   -
% - Anyway, a big thanks for stopping by!                             -
% ---------------------------------------------------------------------

\documentclass[letterpaper,11pt]{article}
\usepackage[margin=.75in,bottom=0.5in,top=1.0in]{geometry}

\usepackage{lastpage}
\usepackage{enumitem}
\usepackage{hyperref}

% ---------------------------------------------------------------------

\newcommand{\authorName}	{Wryn (yage) Wagner}
\newcommand{\phone}		{\textsf{(720) 557-5443}}
\newcommand{\email}		{\textsl{wryn@yage.io}}
\newcommand{\github}		{\textsl{github.com/wrynegade}}
\newcommand{\myMajor}		{Computer Science}
\newcommand{\myMinor}		{Mathematics}

% ---------------------------------------------------------------------

\newcommand{\headerLeft}	{\github}
\newcommand{\headerCenter}	{\begin{huge}\textbf{\authorName\\}\end{huge}\phone}
\newcommand{\headerRight}	{\email}
\newcommand{\pageOfTotal}	{\thepage\ of \pageref{LastPage}}
\usepackage{fancyhdr}
\pagestyle{fancy}
\fancyhf{}
\fancyhead[L]{\headerLeft}
\fancyhead[R]{\headerRight}
\fancyhead[C]{\headerCenter}


\setlength{\parindent}{0em} % Indent Length
\hyphenpenalty=5000%
\begin{document}

% ---------------------------------------------------------------------
% --- Education -------------------------------------------------------
% ---------------------------------------------------------------------

\begin{Large}\textbf{\\Education}\end{Large}

%\textbf{PhD Symbolic Artificial Intelligence}\hfill 2021 to Present\\
%Utah State University, Logan, Utah
%\begin{itemize}[noitemsep,topsep=0pt]
%	\item Emphasis on inference and natural language generation\\
%\end{itemize}

\textbf{B.S. Computer Science with Mathematics Minor}\hfill Graduated December 2020\\
Utah State University, Logan, Utah%\hfill 3.7 GPA
\begin{itemize}[noitemsep,topsep=0pt]
	\item Presidential Scholarship (Academic Full-Tuition)
	% \item Worked 20 to 30 hours per week during the school year while maintaining between 16 and 18 credits\\
\end{itemize}

%\textbf{Relevant Coursework}
%\begin{itemize}[noitemsep,topsep=0pt]
%	\item Discrete Mathematics
%	\item Algorithm Design and Computational Complexity (PhD level)
%	\item Intelligent Systems and Computer Vision
%	\item Agile Software Engineering
%\end{itemize}


% ---------------------------------------------------------------------
% --- Technical and Work Skills ---------------------------------------
% ---------------------------------------------------------------------

\begin{Large}\textbf{\\Technical and Work Skills}\end{Large}

\textbf{Programming Language Proficiency} \\
Python \hfill JavaScript \hfill SH\hfill CLISP\hfill C / C++\hfill C\#\hfill Java\hfill Matlab\hfill PHP\\

\textbf{Software and Technology}\\
Kubernetes\hfill Docker\hfill \LaTeX\hfill ViM\hfill Linux\hfill Django\hfill AWS\hfill Redis\hfill Twilio\hfill Angular\hfill Material Design

\noindent\textbf{Communication and Language}
\begin{itemize}[noitemsep,topsep=0pt]
	\item Value strong communication and embrace team environments
	\item Driven public speaker
	\item Fluent in Spanish both written and oral (formal and idiomatic)
\end{itemize}

% ---------------------------------------------------------------------
% --- Work History ----------------------------------------------------
% ---------------------------------------------------------------------

\begin{Large}\textbf{\\Work History}\end{Large}

\textbf{Directus} \textit{(Logan UT)}. Site Reliability Engineer \hfill April 2022 - Present
\begin{itemize}[noitemsep,topsep=0pt]
	\item Lead R\&D and demonstrate proof of concept for new technology
	\item Design and implement architecture at a global scale
	\item Maintain global server health including on call support for critical system outages
	\item Provide advanced customer support including solutions consulting, infrastructure inspection, and database maintenance\\
\end{itemize}

\textbf{Rent Dynamics} \textit{(Logan UT)}. Site Reliability Engineer \hfill August 2020 - April 2022
\begin{itemize}[noitemsep,topsep=0pt]
	\item Participate in R\&D and demonstrate proof of concept for new technology
	\item Assist in team training for new technology and architecture
	\item Maintain server health including on call support and maintenance for critical system outages
	\item Major Projects \begin{itemize}[noitemsep, topsep=0pt]
		\item Upgrade deprecated stack for a large scale project. Upgraded Linux, Django, PostgreSQL, and performed major refactors to a robust codebase.
		\item Transfer a transactional database interaction to a Redis-based solution on a major traffic endpoint. Included transition from C\# on a Windows server to a load-balanced Django solution backed by Linux. Solution manages millions of transactions per second.
		\item Create and maintain an automated, cross-platform, developer setup script. This keeps our developers' machines up-to-date, and provides a unified solution-base for development.
		\item Containerize applications and create new, automated Kubernetes deployments.\\
	\end{itemize}
\end{itemize}

\textbf{Rent Dynamics} \textit{(Logan UT)}. Junior Software Developer \hfill January 2019 - August 2020
\begin{itemize}[noitemsep,topsep=0pt]
	\item Full-stack development for production-scale lead management software\\ Driven by: Node.js, AngularJS, and React\qquad\quad Backed by: Django, Entity framework (.NET core)
	\item Complete deadlines and communicate as a member of an Agile development team
	\item Major Projects \begin{itemize}[noitemsep, topsep=0pt]
		\item Prototyped, built, and supported a remote, IoT door-traffic counter for client offices. A configured raspberry pi received signals from coin-cell operated sensors and sent a custom-encoded SMS to our database on a daily basis.
		\item Designed, prototyped, and implemented an automated property touring application. Included rapid adaptations in anticipation of the COVID-19 Pandemic, allowing for virtual tour options and the disabling of in-person tours when on-site agents reported exposure to COVID-19.
	\end{itemize}
\end{itemize}

\clearpage
\textbf{Smith's/Starbucks} \textit{(Logan UT)}. Barista \hfill May 2018 - January 2019
\begin{itemize}[noitemsep,topsep=0pt]
	\item Remembered customers' names, tastes, and favorite orders while simultaneously brewing coffee, preparing food, cleaning, and promoting seasonal specials.
	\item Lead and prepared coffee tastings, including pastry or food pairings
	\item Through taste and smell alone, learned to identify a coffee's origin across several world regions\\

\end{itemize}

\textbf{SevOne} \textit{(Highlands Ranch CO)}. Systems Engineer Intern \hfill January 2014 - May 2014
\begin{itemize}[noitemsep,topsep=0pt]
	\item Created a PHP solution to ingest performance data into the SevOne platform for Comcast and Zayo\\
\end{itemize}

\textbf{Mathematics Tutor} \textit{(Highlands Ranch CO)}. \hfill August 2012 - May 2014
\begin{itemize}[noitemsep,topsep=0pt]
	\item Performed one-on-one tutoring for topics of mathematics ranging from Algebra to Calculus
	\item Helped students overcome challenges and achieve high grades by breaking concepts into palpable fundamentals and helping fill students' foundational gaps
	\item Prepared weekly lessons, solidifying my own understanding of groundwork mathematics\\
\end{itemize}

%\textbf{Highlands Ranch Community Association} \textit{Highlands Ranch CO}. Lifeguard II \hfill August 2011 - May 2014
%\begin{itemize}[noitemsep,topsep=0pt]
%	\item Maintained active International Lifeguarding Association license through Ellis and Associates
%	\item Completed weekly life-saving and emergency training
%	\item Rendered immediate first-aid to health incidents throughout the entire facility
%\end{itemize}


% ---------------------------------------------------------------------------------------------
% -- Volunteer History ------------------------------------------------------------------------
% ---------------------------------------------------------------------------------------------

\begin{Large}\textbf{\\Extracurricular}\end{Large}

\textbf{``The Huddle'' (Organization Chair).} \textit{2021 - Present}
\begin{itemize}[noitemsep,topsep=0pt]
	\item Introduce developers and students to open source through activities and presentations.
	\item Develop and maintain community projects.
	\item \url{https://github.com/TheHuddle} and \url{https://codehuddle.org}\\
\end{itemize}

\textbf{Volunteer Service (Rosario, Argentina).} \textit{October 2015 - October 2017}
\begin{itemize}[noitemsep,topsep=0pt]
	\item Provided disaster relief to small \textit{pueblitos} affected by tornadoes and prolonged flooding
	\item Immersed in local culture and built long-lasting connections and friendships
	\item Executed and maintained daily plans and records\\
\end{itemize}

\textbf{HackUSU (Club Board Member).} \textit{2018 Calendar Year}
\begin{itemize}[noitemsep,topsep=0pt]
	\item Prepared and directed the annual Hackathon for Utah State University in 2018
	\item Overhauled and maintained the club website
	\item Formally corresponded with sponsors and performed outreach to potential sponsors\\
\end{itemize}

\textbf{Aggie Game Nights (Club Board Member).} \textit{2018 Calendar Year}
\begin{itemize}[noitemsep,topsep=0pt]
	\item Planned, documented, and attended weekly board meetings
	\item Advertised and hosted a board game tournament quarterly\\
\end{itemize}

%\textbf{Free Software Linux Club (Club Member).} \textit{January 2017 to Present}
%\begin{itemize}[noitemsep,topsep=0pt]
%	\item Explore Linux distributions and contribute to open source projects
%	\item During the summer months, create weekly programming challenges with automated testing
%\end{itemize}


% ---------------------------------------------------------------------------------------------
% -- References -------------------------------------------------------------------------------
% ---------------------------------------------------------------------------------------------

\begin{Large}\textbf{\\References}\end{Large}

\textit{\\available upon request}
%\textbf{Skyler Cain - Former CTO of Rent Dynamics}
%\begin{itemize}[noitemsep,topsep=0pt]
%	\item skylercain@gmail.com \textit{(perferred)}
%	\item \url{https://www.linkedin.com/in/skylercain}\\
%\end{itemize}
%
%\textbf{Levi Howa - VP of Technology of Rent Dynamics}
%\begin{itemize}[noitemsep,topsep=0pt]
%	\item levicusrodcet@gmail.com \textit{(perferred)}
%	\item \url{https://www.linkedin.com/in/levi-howa}\\
%\end{itemize}
%
%\textbf{Haitao Wang - Professor}
%\begin{itemize}[noitemsep,topsep=0pt]
%	\item Haitao.Wang@usu.edu \textit{(perferred)}
%	\item (435) 797-2416\\
%\end{itemize}
%
%\textbf{Josef Wagner - Personal Reference}
%\begin{itemize}[noitemsep,topsep=0pt]
%	\item josefwagnerus@gmail.com \textit{(perferred)}
%	\item (208) 713-3929
%\end{itemize}


% ---------------------------------------------------------------------------------------------
% -- End --------------------------------------------------------------------------------------
% ---------------------------------------------------------------------------------------------

\end{document}
